### 2019-08-06 report/MSc_Report.tex
Grammar, anova tables, discussion

Studies get more attention and are more likely to be published, read and cited if they contain significant effects. Studies with no evidence for an effect are less likely to get published. This generates a bias called ``publication bias'', a distorted view of the evidence for an effect. Publication bias has been identified as one of the major concerns in irreproducible research \citep{Bishop.2019}. The issue has been discussed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}, \citet{Dwan2013}). Consensus is that publication bias exists in clinical science. \\
In medical research, clinical trials study the efficacy of therapies and drugs. The gold standard in such intervention studies are randomized controlled trials (RCTs). Results from RCTs influence the treatment of patients in daily clinical practice. The results from multiple intervention studies can be summarized in a meta-analysis to estimate an overall treatment effect (access all studies) \citep{Cochran}. However, publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm, distortion and financial expenses. \\
There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}).
The authors agree on that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects. Although there are policies that make it mandatory to make all study results publicly accessible \citep{fda}, it is not clear if the situation has improved yet.\\
There are multiple ways to assess the amount of publication bias. For instance, it is possible to follow studies and assess if they are getting published depending on their findings (\citet{Dwan2013}, \citet{publication.fate}, \citet{Lee.2008}). One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in social sciences: \citet{social.sciences.publication.bias}). Another way is to compare results in study registries with results published in journals (\eg \citet{pb.clinicalscience.2013}). Again one finds systematic differences between published and unpublished results. \\
A third way is to assess the so-called small study effect in a meta-analysis, that is, smaller studies sometimes showing different, often larger treatment effects than large ones (cite sb). Importantly, this method does not assess publication bias directly. But the estimation of small study effects is oftentimes the most efficient way to investigate publication bias in a large number of meta-analyses. However, evidence for small study effects can oftentimes be interpreted as evidence for publication bias \citep{Egger}, as this is the most likely cause, even though there may also be other explanations. The underlying rationale is that journal editors are guided by two simple rules (\citet{excess.significance}, \citet{ioannidis.2019}): 
\begin{itemize}
\item Publish new and trend-setting findings that lead to many citations, increasing the journal impact factor (JIF).
\item Publish large trials that are likely to set the standard for a given scientific question, again to increase the JIF.
\end{itemize}

This then leads to an asymmetry in published studies; small studies show larger effect sizes than larger studies do. A funnel plot(cite sb) allows visual inspection of small study effects by plotting the effects against their standard error. For illustration purposes, one meta-analysis with large funnel plot asymmetry and one with no asymmetry is shown in Figure \ref{small.study.effect.examples }. %\citep{pre.eclampsia}: 
By means of simple linear regression, one can investigate how much evidence there is for this asymmetry.

@@

gives the marginal distribution of $\mathbf{y}{_{j}}$ depending on $U{_i}$ and $\epsilon{_{j}}$. The random effects $U{_i} \sim N(0, \mathbf{G})$ and the residual error term $\epsilon{_{j}} \sim N(0, \tau^{2})$ are independent from eahc other. The expectation $\mathbb{E}(\mathbf{y}_{j})$ is still $x_j \beta$, but now, the covariance between the observations within a group $i$, $\mathbf{y}_i$, is modeled as

@@

whith $m$ being the number of groups and $\hat{\mathbf{V}}_i$ being the estimated covariance, obtained by maximizing the log likelihood of the normal distribution, as $\mathbf{y}_i$ is distributed as

@@

Weights can be introduced by replacing $\mathbf{I}_{n_i}$ in \eqref{eq:random.intercepts.covariance} with the previously introduced weight matrix $\mathbf{W}_i$ .Hypothesis tests for $\beta = \beta_\textrm{H0}$ can be made using the wald method.

@@

\begin{align}
\theta_i &= \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
\se_i^2 &= 1/4n_t + /4n_c \nonumber
\end{align}

@@

\section{Small Study Effect and Publication Bias Adjustment}
There are different approaches to correct for small study effects and publication bias. They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (\ie very small standard error) or to a summary effect, corrected for publication bias. Selection models aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:

\subsection{Adjustment by Regression} \label{sec:regression.adjustment}
\citet{limitmeta} use a random effects model %together with shrinkage procedure 
to obtain an unbiased estimate. Similarly to 
%what has been seen in Copas selection model, we let $y_i$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_i}$ as in \eqref{limitmeta.regression}.
regression based tests for small study effects, we have

@@

Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior with respect to coverage (and mean squared error).

@@

$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$-value. Note that the test is almost equivalent to Egger's small study effect test with $\tau^2 = 0$. Thus, although the copas selection model models publication bias, it is dependent on the small study effects to find the most suitable pair $(a,b)$. \\
If one applies the model to a single meta-analysis, a sensitivity analysis is suggested. One can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process. Selection models are in general not recommended for inference (\eg \citet{selection.assessment}). 
\citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. \\
A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied. If all obtained $p$-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for modelling, and the standard, classical random effects meta-analysis is retained. If none of the $p$-values is above the threshold, a wider range of values for $(a,b)$ is used. When some $p$-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the least intense underlying selection model is chosen).\\
Currently, there is no test to detect miss-specifications in the model itself, the authors themselves have argued that a non-parametric test of the residuals would lack power.

@@

Initially, the analysis is restricted to results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}. If \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR}, \texttt{RR}, \texttt{SMD}, \texttt{MD}, \texttt{Hazard Ratio} and \texttt{Rate Ratio} are used. 
\citet{Ioannidis2007} outlined criteria for application of small study effect tests:
\begin{itemize}
\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 9772 remaining). 
\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 9473 remaining).
\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 7452 remaining)
\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 1388 remaining).
\end{itemize}
Additionally, the following criteria have been applied:
\begin{itemize}
\item \textbf{Sensitivity Analyses}: When the same results are used multiple times for different meta-analyses, only one is retained. More precisely, if a study hat the same \texttt{study.name} and same \texttt{effect}, it was considered a duplicate, and the smaller meta-analysis of the two was excluded. The intention is to exclude sensitivity analyses which are operated on subsets of the available results.
\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = 20 out of meta-analyses with at least ten studies).
\item \textbf{No withdrawn reviews}: Reviews that have been withdrawn are not included.
\item \textbf{No adverse effects}: No results of adverse effects of treatment are used for meta-analyses. Exclusion is incomplete because only results with ``adverse'' in the comparison or outcome name could be removed, but not all adverse effect results are classified as such.
\end{itemize}

The results of this reduction of the dataset are shown in the flow-chart in Figure \ref{Inclusion.criteria}. Only the data that had accesible all results data available was used for adjustment. Thus, all meta-analyses with \texttt{outcome.flag} == \texttt{IV} and \texttt{outcome.measure.merged} not equal to \texttt{SMD} are ommitted in a second step of the analysis (Analysis dataset (1) and (2) in Figure \ref{Inclusion.criteria}).

@@

\subsubsection{Exclusions for other Reasons}
In some more cases, meta-analyses were excluded because their results seemed to be erroneous (1) or because participant numbers were missing (5), necessary to compute the variance of Fisher's z transformed correlation coefficient. The latter meta-analyses (all \texttt{outcome.flag} = \texttt{IV}) were only ommitted when doing the adjustment based on the $z$-scores, but kept when adjusting based on std. mean differences. The meta-analysis that is considered erroneous is from a review with the title ``School-based programs for preventing smoking''. The reason why it is suspected to be erroneous is because there are results from one study (Severson, 1991) with rather large effects (13, 0.4, 6.3, 2.4) compared to a mean std. mean difference in 12 other results of 0.22 (max.: 0.91) and very large standard errors (64, 60, 46, 70) compared to a mean \texttt{se} of 0.6 (max.: 3.8). It is not included in the analysis.

\subsubsection{The Analysis Dataset}
The dataset that was ultimately tested and adjusted for publication bias comprises 1 meta-analyses and 22937 results. The mean number of participants in the treatment group is 253.5 vs 256.7 in the unrestricted dataset and the mean total number of participants 589.3 vs 623.2. The mean publication year is 2000.4408025 vs 2000.9711014 in the unrestricted dataset. \\
From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}), there are 36 with \\ \texttt{outcome.measure.merged} = ``Risk Ratio'', 26 ``Std. Mean Difference'',  25 ``Hazard Ratio'' and 15 ``Odds Ratio'' (and 25 additional, different outcome measures).

@@

Meta-analysis groups within a review were obtained by grouping by comparison, outcome and subgroup. The last step is optional, and the Cochrane groups do also meta-analysis without taking into account subgroups. Subgroups are often specificaions of treatment, \eg the form of the medication or the protocoll. Thus, using the subgroups should increase the within-study homogeneity. However, the Cochrane Organisation disencourages meta-analyses based on subgroups only, because subgroups are often set up after the collection of the data analysis. Since the main interest of this study is not to precisely assess the efficacy of treatments, but the interest is merely on systematic differences between single studies investigating the same scientific question and not in the effect per se, it has been decided that the increase in precision is worthwile the loss of a number of studies. While it is possible that the use of subgroups introduces bias in the meta-analysis, it is also possible that ignoring subgroups will do (which is one of the reasons why subgroups are analyses as well). When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails. Subgroups are not indicated in 50.8\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane review groups did.

@@

For applying publication bias tests and adjustment methods, the analysis was applied such that the effects used are similar or identical to the effects on which journal editors decided upon publication bias. For \texttt{outcome.flag} = \texttt{DICH}, log risk ratios were used as treatment effect estimates in the meta-analysis, for \texttt{outcome.flag} = \texttt{CONT}, mean difference or standardised mean difference, depending on \texttt{outcome.measure.merged}. For \texttt{outcome.flag} = \texttt{IV}, the \texttt{effect} and \texttt{se} as provided in the dataset was passed to \texttt{meta::metagen}. \\ 

@@

In the case of the one-sided test procedure (small study effect and excess significance tests), the effect side in which bias was expected had to be prespecified. This was solved by comparing the number of significant findings on each side (original effect scale, i.e. for binary outcomes log risk ratios, \etc); the side with more significant findings (two-sided $p$-value < 0.05) was considered the side of potential bias. If numbers were equal, the side of the fixed effects treatment was used. \\

@@

All compuations were performed in the \texttt{R} computing environment \citep{R.base}. The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments. The excess significance test was adapted from \citet{vanAert.2019}. For data manipulation procedures, the \texttt{tidyverse} packages were used \citep{tidyverse.package}, and for plotting the \texttt{ggplot2} package \citep{ggplot2}.\\

@@

Using Fisher's $z$ transformation, we can transform all effect sizes of the dataset on the same scale such that they are comparable to each other. Thus, as a first step, an exploratory plot of the median effect size and it's dependence on the study sample size can be shown. \\
The absolute value of the median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}. It is clearly visible that the absolute value decreases with increasing sample size, i.e. that the effect size is becoming smaller. The trend flattens off after $\sim$ sample size = 400 (not shown). \\
The pattern is similar in Figure \ref{effect.samplesize.separated}, where the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std. Mean Difference'' are used (the most common measurs in the dataset). Here, the effect sizes are scaled (mean subtraction and divison through standard error) with respect to all other effects of the same measure.

@@

The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small publication bias tests and excess significance tests. The direction in which bias is expected is the one on which more significant results are ($p$-value < 0.05, two-sided). The tests are applied on the original effect size measures, since the journal editors and the researchers also base their decisions on them. Different tests are applied depending on the outcome being binary or continuous.\\
Multiple tests are applied on the same data to compare their results. A histogram of $p$-values for each test and all meta-analyses will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}. Skewedness indicates evidence for publication bias.\\
The abbreviations in Figure \ref{fig:test}  are shortly explained with references to chapter \ref{ch:methods}: \\
``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}. For continuous and \texttt{IV} outcomes, the names refer to:

@@

\end{knitrout}
\caption{Histogram of one-sided $p$-values for small study effect in direction of larger effect sizes. The testing method is indicated in the header, bin width is equal to 0.1. The proportion of meta-analyses with signifiant publication bias based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test}
\end{figure}

%Agreement table -> Chunck 1
The histograms in Figure \ref{fig:test} show that the tests are not alway in agreement if publication bias is present in the data. The $p$-values of excess significance and Schwarzer's test and the $p$-values for \texttt{IV} outcomes are rather uniformly distributed, or even skewed to the right. Notably, excess significance test, Schwarzer's test and rank tests have been shown to lack power. The tests that are more suitable (regression based tests in general) all have proportions of significant $p$-values ($p$ > 0.1) clearly above 10 \% which would be the expected false positive rate.\\
In Figure \ref{fig:test}, the meta-analyses with an estimated $I^2$ of zero are depicted, because some methods are known to only be suitable when no heterogeneity is present (excess significance test and also Egger's test). Others are specially constructed to adjust for between study heterogeneity (Thompson and Sharp's test and R\"ucker's test). In continuous outcomes, when Thompson and Sharp's test is applied, the evidence for publication bias decreases, as can be seen in the smaller proportion of blue on the left corner in Figure \ref{fig:test}. However, this is also due to application to meta-analyses with $I^2$ equal zero, in which case the method is known to lack power. Similarly, the evidence decreases somewhat when R\"ucker's test is extended by Thompson and Sharp's method to account for heterogeneity. The moderate decrease indicates however that the previous restriction to meta-analyses with $I^2 < 0.5$ is sufficient to remove meta-analyses with large heterogeneity and that the test results are not heavily influenced by unaccounted between study heterogeneity. \\
The $p$-values of tests can be summarized by computing their harmonic mean. In the case of binary tests, the $p$-values of R\"ucker's, Peters, Harbord's, Schwarzer's and excess significance tests are used, in the case of continuous and \texttt{outcome.flag} = \texttt{IV} outcomes, Egger's, Thompson and Sharp's, Begg and Mazumdar's and excess significance tests are used. This lead's to an overall of 20.3\% significant results ($p_\textrm{harmonic}$ < 0.1, 19.7\% \texttt{outcome.flag} = \texttt{DICH}, 20.1\% \texttt{outcome.flag} = \texttt{CONT}, 25.6\% \texttt{outcome.flag} = \texttt{IV}).

@@

We can see that in some occasions, the method finds more than half of all studies are missing. In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}. The discrepancy between mean and median may indicate that the estimate of 11.4\% missing studies depends somewhat on these extreme cases. As can be written of from Table \ref{copas.missing}, 5\%, \ie 28 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 1,060, more than 30\% of missing studies.

>>>>

Studies get more attention and are more likely to be published, read and cited if they contain significant effects. Studies with no evidence for an effect are less likely to get published. This generates a bias called ``publication bias'', a distorted view of the evidence for an effect. Publication bias has been identified as one of the major concerns in irreproducible research \citep{Bishop.2019}. The issue has been discussed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}, \citet{Dwan2013}). Consensus is that publication bias exists in clinical science. \\
In medical research, clinical trials study the efficacy of therapies and drugs. The gold standard in such intervention studies are randomized controlled trials (RCTs). Results from RCTs influence the treatment of patients in daily clinical practice. The results from multiple intervention studies can be summarized in a meta-analysis to estimate an overall treatment effect (access all studies) \citep{Cochran}. However, publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm, distortion and financial expenses. \\
There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}).
The authors agree on that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects. Although there are policies that make it mandatory to make all study results publicly accessible \citep{fda}, it is not clear if the situation has improved yet.\\
There are multiple ways to assess the amount of publication bias. For instance, it is possible to follow studies and assess if they are getting published depending on their findings (\citet{Dwan2013}, \citet{publication.fate}, \citet{Lee.2008}). One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in the social sciences: \citet{social.sciences.publication.bias}). Another way is to compare results in study registries with results published in journals (\eg \citet{pb.clinicalscience.2013}). Again one finds systematic differences between published and unpublished results. \\
A third way is to assess the so-called small study effect in a meta-analysis, that is, smaller studies sometimes showing different, often larger treatment effects than large ones (cite sb). Importantly, this method does not assess publication bias directly. But the estimation of small study effects is oftentimes the most efficient way to investigate publication bias in a large number of meta-analyses. However, evidence for small study effects can oftentimes be interpreted as evidence for publication bias \citep{Egger}, as this is the most likely cause, even though there may also be other explanations. The underlying rationale is that journal editors are guided by two simple rules (\citet{excess.significance}, \citet{ioannidis.2019}): 
\begin{itemize}
\item Publish new and trend-setting positive findings that lead to many citations, increasing the journal impact factor (JIF). Statistically significant effects are oftentimes interpreted as confirming an effect.
\item Publish large trials that are likely to set the standard for a given scientific question, again to increase the JIF.
\end{itemize}

Publication bias thus leads to larger effects in studies with larger uncertainities, in order for them to be statistically significant. A funnel plot \citep{funnel.plot} allows visual inspection of small study effects by plotting the effects against their standard error. For illustration purposes, one meta-analysis with large funnel plot asymmetry and one with no asymmetry is shown in Figure \ref{small.study.effect.examples }. %\citep{pre.eclampsia}: 
By means of simple linear regression, one can investigate how much evidence there is for this asymmetry.

@@

gives the marginal distribution of $\mathbf{y}{_{j}}$ depending on $U{_i}$ and $\epsilon{_{j}}$. The random effects $U{_i} \sim N(0, \mathbf{G})$ and the residual error term $\epsilon{_{j}} \sim N(0, \tau^{2})$ are independent from each other. The expectation $\mathbb{E}(\mathbf{y}_{j})$ is still $x_j \beta$, but now, the covariance between the observations within a group $i$, $\mathbf{y}_i$, is modeled as

@@

with $m$ being the number of groups and $\hat{\mathbf{V}}_i$ being the estimated covariance, obtained by maximizing the log likelihood of the normal distribution, as $\mathbf{y}_i$ is distributed as

@@

Weights can be introduced by replacing $\mathbf{I}_{n_i}$ in \eqref{eq:random.intercepts.covariance} with the previously introduced weight matrix $\mathbf{W}_i$ .Hypothesis tests for $\beta = \beta_\textrm{H0}$ can be made using the Wald method.

@@

\begin{align}
\theta_i &= \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
\se_i^2 &= 1/4n_t + 1/4n_c \nonumber
\end{align}

@@

\section{Publication Bias Adjustment}
There are different approaches to correct for small study effects and publication bias. They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (\ie very small standard error) or to a summary effect, corrected for publication bias. Selection models aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:

\subsection{Adjustment by Regression} \label{sec:regression.adjustment}
In \citet{limitmeta.2} and \citet{limitmeta}, a random effects model is proposed to obtain unbiased treatment effect estimates. Similarly to regression based tests for small study effects, we have

@@

Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior to the former, because it showed a smaller mean-squared error in simulation studies \citet{limitmeta.2}. Also, this simulation study emphasizes that adjustment is more reliable when effects of publication bias are strong within a meta-analysis. When no publication bias affects the meta-analysis, and event rates are low, the method will provide biased estimates and the mean squared error is large. Coverage of the confidence is always larger or equal to meta-analysis. It outperforms or is equal to classical meta-analysis estimates if there is publication bias, especially if event rates in the control group are small.

@@

$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$-value. Note that the test is almost equivalent to Egger's small study effect test with $\tau^2 = 0$. Thus, although the copas selection model models publication bias, it is dependent on the small study effects to find the most suitable pair $(a,b)$. \\
If one applies the model to a single meta-analysis, a sensitivity analysis is suggested. One can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process. Selection models are in general not recommended for inference (\eg \citet{selection.assessment}). 
\citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. However, in the simulations, the method was outperformed by the regression adjustment method when publication bias was present. Especially when event rates in the control group were small and publication bias was strong, bias, mean squared error and coverage was substantially worse.\\
A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied. If all obtained $p$-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for modelling, and the standard, classical random effects meta-analysis is retained. If none of the $p$-values is above the threshold, a wider range of values for $(a,b)$ is used. When some $p$-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the least intense underlying selection model is chosen).\\
Currently, there is no test to detect miss-specifications in the model itself, the authors themselves have argued that a non-parametric test of the residuals would lack power.

@@

Initially, the analysis is restricted to results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}. If \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR} / \texttt{RR} / \texttt{SMD} / \texttt{MD} / \texttt{Hazard Ratio} / \texttt{Rate Ratio} are used. 
\citet{Ioannidis2007} outlined criteria for application of small study effect tests:
\begin{itemize}
\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 9772 remaining). 
\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 9473 remaining).
\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 7452 remaining)
\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 1388 remaining).
\end{itemize}
Additionally, the following criteria have been applied:
\begin{itemize}
\item \textbf{Sensitivity Analyses}: When the same results are used multiple times for different meta-analyses, only one is retained. More precisely, if a study hat the same \texttt{study.name} and same \texttt{effect}, it was considered a duplicate, and the smaller meta-analysis of the two was excluded. The intention is to exclude sensitivity analyses which are operated on subsets of the available results.
\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = 20 out of meta-analyses with at least ten studies).
\item \textbf{No withdrawn reviews}: Reviews that have been withdrawn are not included.
\item \textbf{No adverse effects}: No results of adverse effects of treatment are used for meta-analyses. Exclusion is incomplete because only results with ``adverse'' in the comparison or outcome name could be removed, but not all adverse effect results are classified as such.
\end{itemize}

The results of this reduction of the dataset are shown in the flow-chart in Figure \ref{Inclusion.criteria}. Only the data that had accessible all results data available was used for adjustment. Thus, all meta-analyses with \texttt{outcome.flag} == \texttt{IV} and \texttt{outcome.measure.merged} not equal to \texttt{SMD} are omitted in a second step of the analysis (Analysis dataset (1) and (2) in Figure \ref{Inclusion.criteria}).

@@

\subsubsection{Exclusions for other Reasons}
In some more cases, meta-analyses were excluded because their results seemed to be erroneous (1) or because participant numbers were missing (5), necessary to compute the variance of Fisher's z transformed correlation coefficient. The latter meta-analyses (all \texttt{outcome.flag} = \texttt{IV}) were only omitted when doing the adjustment based on the $z$-scores, but kept when adjusting based on std. mean differences. The meta-analysis that is considered erroneous is from a review with the title ``School-based programs for preventing smoking''. The reason why it is suspected to be erroneous is because there are results from one study (Severson, 1991) with rather large effects (13, 0.4, 6.3, 2.4) compared to a mean std. mean difference in 12 other results of 0.22 (max.: 0.91) and very large standard errors (64, 60, 46, 70) compared to a mean \texttt{se} of 0.6 (max.: 3.8). It is not included in the analysis.

\subsubsection{The Analysis Dataset}
The dataset that was ultimately tested and adjusted for publication bias comprises 1388 meta-analyses and 22,937 results. The mean number of participants in the treatment group is 253.5 vs 256.7 in the unrestricted dataset and the mean total number of participants 589.3 vs 623.2. The mean publication year is 2000 vs 2001 in the unrestricted dataset. \\
From the meta-analyses with incomplete data (\texttt{outcome.flag} == \texttt{IV}), there are 36 with \\ \texttt{outcome.measure.merged} = \texttt{RR}, 26 \texttt{SMD},  25 \texttt{Hazard Ratio}, 15 \texttt{OR}, 11 \texttt{MD} and 8 \texttt{Rate Ratio}.

@@

Meta-analysis groups within a review were obtained by grouping by comparison, outcome and subgroup. The last step is optional, and the Cochrane groups do also meta-analysis without taking into account subgroups. Subgroups are often specifications of treatment, \eg the form of the medication or the protocol. Thus, using the subgroups should increase the within-study homogeneity. However, the Cochrane Organisation disencourages meta-analyses based on subgroups only, because subgroups are often set up after the collection of the data analysis. Since the main interest of this study is not to precisely assess the efficacy of treatments, but the interest is merely on systematic differences between single studies investigating the same scientific question and not in the effect per se, it has been decided that the increase in precision is worthwhile the loss of a number of studies. While it is possible that the use of subgroups introduces bias in the meta-analysis, it is also possible that ignoring subgroups will do (which is one of the reasons why subgroups are analyses as well). When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails. Subgroups are not indicated in 50.8\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane review groups did.

@@

For applying publication bias tests and adjustment methods, the analysis was applied such that the effects used are similar or identical to the effects on which journal editors decided upon publication bias. For \texttt{outcome.flag} = \texttt{DICH}, log risk ratios were used as treatment effect estimates in the meta-analysis, for \texttt{outcome.flag} = \texttt{CONT}, mean difference or standardized mean difference, depending on \texttt{outcome.measure.merged}. For \texttt{outcome.flag} = \texttt{IV}, the \texttt{effect} and \texttt{se} as provided in the dataset was passed to \texttt{meta::metagen}. Since the intuition behind small study effect tests is that effects with larger standard errors have to be larger to reach significance, the publication bias tests and adjustments are most meaningful if the effects are used in their original scale. Transformation will change the relative size of uncertainty estimates and effects.\\ 

@@

In the case of the one-sided test procedure (small study effect and excess significance tests), the effect side in which bias was expected had to be pre-specified. This was solved by comparing the number of significant findings on each side (original effect scale, i.e. for binary outcomes log risk ratios, \etc); the side with more significant findings (two-sided $p$-value < 0.05) was considered the side of potential bias. If numbers were equal, the side of the fixed effects treatment was used. \\

@@

All computations were performed in the \texttt{R} computing environment \citep{R.base}. The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments. The excess significance test was adapted from \citet{vanAert.2019}. For data manipulation procedures, the \texttt{tidyverse} packages were used \citep{tidyverse.package}, and for plotting the \texttt{ggplot2} package \citep{ggplot2}.\\

@@

Using Fisher's $z$ transformation, we can transform all effect sizes of the dataset on the same scale such that they are comparable to each other. Thus, as a first step, an exploratory plot of the median effect size and it's dependence on the study sample size can be shown. \\
The absolute value of the median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}. It is clearly visible that the absolute value decreases with increasing sample size, i.e. that the effect size is becoming smaller. The trend flattens off after $\sim$ sample size = 400 (not shown). \\
The pattern is similar in Figure \ref{effect.samplesize.separated}, where the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std. Mean Difference'' are used (the most common measures in the dataset). Here, the effect sizes are scaled (mean subtraction and division through standard error) with respect to all other effects of the same measure.

@@

The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small publication bias tests and excess significance tests. The direction in which bias is expected is the one on which more significant results are ($p$-value < 0.05, two-sided). The tests are applied on the original effect size measures, since the journal editors and the researchers also base their decisions on them. Different tests are applied depending on the outcome being binary or continuous or if the data is only partially available.\\
Multiple tests are applied in order to compare their results. A histogram of $p$-values for each test will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.\\
The abbreviations in Figure \ref{fig:test}  are shortly explained with references to chapter \ref{ch:methods}: \\
``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}. For continuous and \texttt{IV} outcomes, the names refer to:

@@

\end{knitrout}
\caption{Histogram of one-sided $p$-values for small study effect in direction of larger effect sizes. The testing method is indicated in the header, bin width is equal to 0.1. The proportion of meta-analyses with significant publication bias based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test}
\end{figure}

%Agreement table -> Chunck 1
The histograms in Figure \ref{fig:test} show that the tests do not coherently find evidence for publication bias in the dataset. The $p$-values of excess significance and Schwarzer's test are rather uniformly distributed. Notably, excess significance test, Schwarzer's test and rank tests have been shown to lack power. The tests that are more suitable (regression based tests in general) all have proportions of significant $p$-values ($p$ > 0.1) clearly above 10 \% which would be the expected false positive rate.\\
In Figure \ref{fig:test}, the meta-analyses with an estimated $I^2$ of zero are depicted, because some methods are known to only be suitable when no heterogeneity is present (excess significance test and also Egger's test). Other tests are specially constructed to adjust for between study heterogeneity (Thompson and Sharp's test and R\"ucker's test). It can be seen that these tests find a smaller proportion of significant results in Figure \ref{fig:test}. However, this is also due to application to meta-analyses with no between-study heterogeneity, where the methods lack statistical power. Similarly, the evidence decreases somewhat when R\"ucker's test is extended by Thompson and Sharp's method to account for heterogeneity. The moderate decrease indicates however that the previous restriction to meta-analyses with $I^2 < 0.5$ is sufficient to remove meta-analyses with large heterogeneity and that the test results are not heavily influenced by unaccounted between-study heterogeneity.\\
The $p$-values of tests can be summarized by computing their harmonic mean. In the case of binary tests, the $p$-values of R\"ucker's, Peters, Harbord's, Schwarzer's and excess significance tests are used, in the case of continuous and \texttt{outcome.flag} = \texttt{IV} outcomes, Egger's, Thompson and Sharp's, Begg and Mazumdar's and excess significance tests are used. This lead's to an overall of 20.3\% significant results ($p_\textrm{harmonic}$ < 0.1, 19.7\% \texttt{outcome.flag} = \texttt{DICH}, 20.1\% \texttt{outcome.flag} = \texttt{CONT}, 25.6\% \texttt{outcome.flag} = \texttt{IV}).

@@

We can see that in some occasions, the method finds more than half of all studies are missing. In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}. The discrepancy between mean and median may indicate that the estimate of 0\% missing studies depends somewhat on these extreme cases. As can be written of from Table \ref{copas.missing}, 5\%, \ie 0 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 0, more than 30\% of missing studies.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Aug  6 17:32:32 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lrrrrrrr}
  \hline
 & = 0 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
  \hline
Missing fraction & 226 & 0 & 0 & 0.1 & 0.4 & 1.0 & 0.3 \\ 
  Missing study number & 226 & 0 & 0 & 1.5 & 5.9 & 20.1 & 4.7 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.} 
\label{copas.missing}
\end{table}
